### 2021-04-24 nih2/NIHGrant.tex
Add to Approach

\hyphenation{ionto-pho-re-tic iso-tro-pic fortran} % Specifies custom hyphenation points for words or words that shouldn't be hyphenated at all

@@

In the proposed project, we will use reverse correlation to reveal unbiased high-dimensional
representations of tinnitus and further characterize the condition
using dimensionality-reduction and density-based clustering.
In \emph{Aim \#1}, we will develop and run an experimental paradigm
in which tinnitus patients listen to noisy stimuli and perform an alternate forced-choice task
answering the question, ``Does this sound like your tinnitus?''
In \emph{Aim \#2},

>>>>

\hyphenation{ionto-pho-re-tic iso-tro-pic fortran} % Specifies custom hyphenation points for words or words that shouldn't be hyphenated at all
\def\eg{{\emph{e.g.,}}~}
\def\ie{{\emph{i.e.,}}~}

@@

In the proposed project, we will use reverse correlation to reveal unbiased high-dimensional
representations of tinnitus and further characterize the condition
using dimensionality-reduction and density-based clustering.
In \emph{Aim \#1}, we will develop and run an experimental paradigm
in which tinnitus patients listen to noisy stimuli and perform an alternate forced-choice task
answering the question, ``Does this sound like your tinnitus?''
Reverse correlation frees us from the methodological constraint of imposing strong \emph{a priori}
assumptions about the tinnitus percept.
In \emph{Aim \#2}, we will develop an open-source signal processing pipeline
to reconstruct cognitive representations of tinnitus using compressive sensing.
Compressive sensing holds promise to dramatically reduce the number of samples
needed for accurate reconstruction, enabling us to run more experimental subjects for Aim \#1,
and retest subjects to examine the stability of cognitive representations of tinnitus over time.
\emph{Aim \#3} contextualizes reconstructed cognitive representations of tinnitus
by visualizing underlying subtypes or clusters on a lower dimensional manifold.
We will employ dimensionality reduction and clustering algorithms to represent and visualize the data,
providing direct insight into commonalities and variability of tinnitus experience in and between subjects.

\begin{description}
	\item[C.1. Aim \#1]{Uncover and reconstruct cognitive representations of tinnitus} 
\end{description}

In this aim, we will identify high-dimensional cognitive representations of tinnitus using reverse correlation.
Current methods for estimating cognitive representations of tinnitus fall broadly into two primary categories,
each of which has limitations.
One approach is to use forced-choice selection tasks.
In this experimental paradigm,
the experimenter presents participants with multiple samples of auditory stimuli that vary in well-characterized
and often highly-constrained ways, along specific dimensions (\eg pure tone frequency, width of spectral envelope)
that are known to be, or are hypothesized to be, relevant to tinnitus representation or masking
\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021}.
The subject then makes a choice between stimuli.
While new methodological advances in experiment design and technology have streamlined this approach
\cite{korthOneStepCloser2020,henryComputerautomatedTinnitusAssessment2004,henryComputerautomatedTinnitusAssessment2013},
it is still constrained by \emph{a priori} assumptions about the nature of tinnitus percepts.
In contrast, likeness approaches use subjective judgment tasks,
in which the subject rates how much (if at all) a presented stimulus is part of or masks their tinnitus percept
\cite{norenaPsychoacousticCharacterizationTinnitus2002}.
While likeness measures provide more complete reconstructions of tinnitus cognitive representations,
likeness tests are time-consuming and generally not used in clinical practice
\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021}.

The highly-constrained nature of stimuli used in the forced selection approach necessarily results
in recovered representations that are correspondingly constrained and typically low-dimensional. It has
long been known, however, that representations limited to only a few dimensions are insufficient to
account for the full richness of tinnitus experiences
\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021}.
Subjective judgment experiments yield more informative reconstructions but are time-consuming to employ.
The nature of subjective judgment
approach is such that it is best suited to uncover relations between perceptual categories, rather than
characterizing cognitive representations directly, and thus provides limited information about how
perceptual similarity comes about. While some of the recovered dimensions along which stimuli differ in
these tasks correlate with frequently assumed dimensions of representation (\eg frequency and pitch to mask tinnitus percept),
some recovered dimensions of contrast have no known characterization.
Moreover, this approach is fundamentally limited by the precise stimuli presented to participants, and
therefore may not systematically explore the entire space of perceptually-meaningful variables.
